MSc Thesis

### 2023-04-29 manuscript/main.tex
more juli comments. Prepare for merge conflict

18 hours after treatment application, we harvested three fully expanded upper leaves the plants, and split the leaves in half along the midvein. We placed one half of the tissue into a coin envelope, oven dried it for 4 days at 60\degree C, transferred it to a 2ml microcentrifuge tube with three 3.2 mm diameter steel beads, and ground it into a fine powder using a tisselyser (60 seconds at 30 Hz) in preparation for XRF analysis. We placed the other half of the tissue into a microcentrifugre tube, flash froze it in liquid nitrogen, and subsequently freeze dried it. After freeze drying, the samples for phenolic processing were ground under the same conditions as the other samples.

@@

To measure the silicon content of the leaf tissue, we followed a modified version of the bench-top XRF method (\cite{reidinger_rapid_2012}). We pressed leaf powder in a hydraulic press at 11 tons of pressure, using a 13mm die to create a pellet. We then placed the pellet in an Olymus Vanta pXRF mounted in a benchtop stand, and used a 45 second scan time to quantify silicon. After each use, we cleaned the pellet die and XRF analyzer to minimize contamination between samples.

>>>>

We harvested three fully expanded upper leaves the plants, and split the leaves in half along the midvein, 18 hours after treatment application. We placed one half of the tissue into a coin envelope, oven dried it for 4 days at 60\degree C, transferred it to a 2ml microcentrifuge tube with three 3.2 mm diameter steel beads, and ground it into a fine powder using a tisselyser (60 seconds at 30 Hz) in preparation for silicon content analysis. We placed the other half of the tissue into a microcentrifugre tube, flash froze it in liquid nitrogen, and subsequently freeze dried it. After freeze drying, the samples for phenolic processing were ground under the same conditions as the other samples.

@@

To measure the silicon content of the leaf tissue, we followed a modified version of the bench-top x-ray fluorescence (XRF) method (\cite{reidinger_rapid_2012}). We pressed leaf powder in a hydraulic press at 11 tons of pressure, using a 13mm die to create a pellet. We then placed the pellet in an Olymus Vanta pXRF mounted in a benchtop stand, and used a 45 second scan time to quantify silicon. After each use, we cleaned the pellet die and XRF analyzer to minimize contamination between samples.
